Proof equivalence in MLL is PSPACE-complete

### 2015-02-01 main/LMCS.tex
minor edits

The result that a canonical representation of multiplicative linear logic is essentially unfeasible raises the question, whether to turn to alternative notions of identity of proofs than that given by $*$-autonomous categories. The literature offers several interesting directions, including but not limited to \emph{polarised proof nets} \cite{Laurent-1999}, \emph{focused proof nets} \cite{Andreoli-Maieli-1999}, \emph{multi-focused proofs} \cite{Chaudhuri-Miller-Saurin-2008}, and Paul-Andr\'e Melli\`s's semantically appealing tensorial logic and dialogue categories \cite{Mellies-2012}.

@@

We would like to thank Lutz Stra{\ss}burger for taking a very careful look at our construction and our proofs, and Dominic Hughes for useful suggestions on exposition.
% and the anonymous referees for their constructive observations.

>>>>

The result that a canonical representation of multiplicative linear logic is essentially unfeasible raises the question, whether to turn to alternative notions of identity of proofs than that given by $*$-autonomous categories. The literature offers several interesting directions, including but not limited to \emph{polarised proof nets} \cite{Laurent-1999}, \emph{focused proof nets} \cite{Andreoli-Maieli-1999}, \emph{multi-focused proofs} \cite{Chaudhuri-Miller-Saurin-2008}, and Paul-Andr\'e Melli\`es's semantically appealing tensorial logic and dialogue categories \cite{Mellies-2012}.

@@

\subsection*{Acknowledgements}
We would like to thank Lutz Stra{\ss}burger for taking a very careful look at our construction, and Dominic Hughes for useful suggestions on exposition.
% and the anonymous referees for their constructive observations.
